---
title: "Assignment 2"
author: "Ying Wu, Yixuan Wang, Ruchika Venkateswaran"
date: "19/06/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
df <- fread('PS1-4003988.csv')
```
1. What is the standard deviation of sales (not past_sales) in the treatment group among
exposed users who saw the campaign in “PS1-4003988.csv” (from Assignment #1)?
Use this number for your calculations below. (5 points)

```{r}
sd1 <- sd(df[Treatment == 1 & saw_ads==1, sales])
sd1
```

2. Suppose you have the budget to spend $0.01 per person on advertising. As your
‘reasonable signal’ or benchmark ad lift, you assume that the campaign will break
even (0 profit).

a. If your profitability margin on sales is 50%, what is the `reasonable signal’ for ad
lift that you are assuming? (2 points)

```{r}
#campaign lift * profitability margin - campaign cost = 0
camp_lift <- (500000*0.01)/0.5
camp_lift

camp_lift_per_person <- camp_lift/500000
camp_lift_per_person
```
The reasonable signal of ad lift would be 10,000, and the incremental sales effect per person would be 0.02. 

b. For a 95% confidence interval, calculate the statistical power to successfully detect
the signal for the following three experimental designs (9 points):

i. 20% of users are assigned to the control group
```{r}
library(pwr)

power1 <- pwr.t2n.test(d=camp_lift_per_person/sd1, n1=0.2*500000, n2=0.8*500000)
power1
```
The statistical power is 14.71% for 20% of users are assigned to the control group. 

ii. 30% of users are assigned to the control group
```{r}
power2 <- pwr.t2n.test(d=camp_lift_per_person/sd1, n1=0.3*500000, n2=0.7*500000)
power2
```
The statistical power is 17.83% for 30% of users are assigned to the control group. 

iii. 80% of users are assigned to the control group
```{r}
power3 <- pwr.t2n.test(d=camp_lift_per_person/sd1, n1=0.8*500000, n2=0.2*500000)
power3
```
The statistical power is 14.71% for 80% of users are assigned to the control group.

Which design is best according to this criterion? (1 point)

The design with 30% of the users assigned to the control group is the best because its statistical power is higher than the other 2 designs with 20% and 80% of the users assigned to the control group respectively (the statistical power for the design with 30% of the users assigned to the control group is 3.12% higher than that of the other two designs). That's why the one with 30% of users assigned to the control group is the best according to the statistical power. 

c. Design i – iii may not be the ‘optimal’ design. What treatment assignment (%
assigned to the control group) maximizes statistical power? (5 points)

```{r}
power4 <- pwr.t2n.test(d=camp_lift_per_person/sd1, n1=0.5*500000, n2=0.5*500000)
power4
```
The optimal design that we recommend is allocating a 50-50 split between the assignment of people. This is because when the treatment & control have equal variances, a 50-50 split gives you the maximum power for a given sample size. The statistical power is around 20.34%.

3. Now suppose instead that you have a fixed ad budget of $2,000 to spend on your own
ads. You ignore the cost of control ads because your partner publisher is providing
them for free.

a. Calculate the average ad spend per person for the three experimental designs
above. Report your answer to 4 decimals. (6 points)
```{r}
e1 <- round((2000/(0.8*500000)),4)
e2 <- round((2000/(0.7*500000)),4)
e3 <- round((2000/(0.2*500000)),4)

cat('The average ad spend per person for the 1st experiment with 80% of the users assigned to the treatment group is: $', e1,'\n',
    'The average ad spend per person for the 2nd experiment with 70% of the users assigned to the treatment group is: $', e2,'\n',
    'The average ad spend per person for the 3rd experiment with 20% of the users assigned to the treatment group is: $', e3,'\n')
```

b. Maintaining your assumption that the campaign will break-even for each
experimental design, what is the ‘reasonable signal’ for each of the three designs
above? Report your answer to 4 decimals. (6 points)
```{r}
lift1 <- 2000/0.5

incre1 <- lift1/(0.8*500000)
incre2 <- lift1/(0.7*500000)
incre3 <- lift1/(0.2*500000)

cat('The ‘reasonable signal’ for the 1st experiment with 80% of the users assigned to the treatment group is: ', incre1,'\n',
    'The ‘reasonable signal’ for the 2nd experiment with 70% of the users assigned to the treatment group is: ', incre2,'\n',
    'The ‘reasonable signal’ for the 3rd experiment with 20% of the users assigned to the treatment group is: ', incre3,'\n')
```

c. For a 95% confidence interval, what is the statistical power now for each of the
three possible experimental designs? Which is highest now? (9 points)
```{r}
power_e1 <- pwr.t2n.test(d=incre1/sd1, n1=0.2*500000, n2=0.8*500000)
power_e2 <- pwr.t2n.test(d=incre2/sd1, n1=0.3*500000, n2=0.7*500000)
power_e3 <- pwr.t2n.test(d=incre3/sd1, n1=0.8*500000, n2=0.2*500000)

power_e1
power_e2
power_e3

cat('The statistical power for the 1st experiment with 80% of the users assigned to the treatment group is: ', '7.36%','\n',
    'The statistical power for the 2nd experiment with 70% of the users assigned to the treatment group is: ', '9.07%','\n',
    'The statistical power for the 3rd experiment with 20% of the users assigned to the treatment group is: ', '43.78%','\n')
```

d. What changes your answer between 2(b) and 3(c)? Which is the best of the six
options in terms of statistical power? (5 points)

The statistical power decreases for the first two experimental designs but increases for the third experiment. It decreases by 7.35% for the first experiment, decreases by 8.76% for the second experiment but increases by 29.07% for the third experiment. The experiment with 20% of the users in the treatment group, given that a fixed ad budget of $2,000 is spent on ads is the most successful experiment with the highest statistical power at 43.78%.

4. You have been thinking about the possibility your ads may wear out so that their
effectiveness decreases as you increase the average ad spend. You revisit your
previous assumption and instead assume the following for the 3 possible experimental
designs:

a. What is the `reasonable' signal now? Fill out the above table. Report your answer to
4 decimals. (6 points)
```{r}
e1_new <- e1*2
e2_new <- e2*1.9
e3_new <- e3*1.2

incre1_new <- round((e1_new/0.5),4)
incre2_new <- round((e2_new/0.5),4)
incre3_new <- round((e3_new/0.5),4)

tab <- matrix(c('From 3(a)', '2x cost=0.02', 'From 3(a)', '1.9x cost=0.0217', 'From 3(a)', '1.2x cost=0.048'), ncol=2, byrow=TRUE)
colnames(tab) <- c('Cost Per Person','Reasonable signal')
rownames(tab) <- c('20% control','30% control','80% control')
tab <- as.table(tab)
tab

cat('----------------------------------------------------------------','\n')

cat('The ‘reasonable signal’ for the 1st experiment with 80% of the users assigned to the treatment group is: ', incre1_new,'\n',
    'The ‘reasonable signal’ for the 2nd experiment with 70% of the users assigned to the treatment group is: ', incre2_new,'\n',
    'The ‘reasonable signal’ for the 3rd experiment with 20% of the users assigned to the treatment group is: ', incre3_new,'\n')

```

b. Under your revised assumption, what is the statistical power of each option? (9
points) Which is best now? (1 point)
```{r}
power_e1_new <- pwr.t2n.test(d=incre1_new/sd1, n1=0.2*500000, n2=0.8*500000)
power_e2_new <- pwr.t2n.test(d=incre2_new/sd1, n1=0.3*500000, n2=0.7*500000)
power_e3_new <- pwr.t2n.test(d=incre3_new/sd1, n1=0.8*500000, n2=0.2*500000)

power_e1_new
power_e2_new
power_e3_new

cat('The statistical power for the 1st experiment with 80% of the users assigned to the treatment group is: ', power_e1_new$power,'\n',
    'The statistical power for the 2nd experiment with 70% of the users assigned to the treatment group is: ', power_e2_new$power,'\n',
    'The statistical power for the 3rd experiment with 20% of the users assigned to the treatment group is: ', power_e3_new$power,'\n')
```
The experiment with 20% of the users in the treatment group has the highest statistical power (58.08%) among the three experiments. 

5.a. You budget $40,000 weekly for the paid search campaign. For your power
calculation, you expect the search ads to generate a lift equivalent to 3X the ad cost.
What is the expected ad lift for the average store (the `reasonable’ signal)? (2
points)



b. Across the 60 locations, the stores have the same average weekly sales of $200,000
with standard deviation $30,000. Given this and using a 90% confidence interval
as your standard, calculate the statistical power for this experiment if you run it
for a single week. (6 points)



c. At current spending levels, how many weeks would you need to run this
experiment before the statistical power of the experiment surpasses 50%? (8
points)


6.a. Given the response rates, how many surveys do you expect to collect in each of
the treatment and control groups? (2 points)





b. DynamicLogic survey proposal is expensive and you can only pay them for this
one ad campaign. What is the likelihood that the 95% confidence intervals on your
ad effect estimates exclude 0 for each survey measure?
i. Brand favorability (3 points)
ii. Purchase intent (3 points)



c. In a one-paragraph summary for a coworker, explain your decision on whether to
use DynamicLogic’s services. Be sure to discuss the strengths and limitations of
survey analysis and explain implications of your power calculation for the
experiment. (6 points)




d. Suppose that 0.5% of users who see the treatment ad fill out the survey, but 0.1%
of users who see the control ad fill the survey. How would this affect your
interpretation of the experimental results? (6 points)












































