---
title: "ba860_a1"
author: "Ying Wu (U30529371)"
date: "09/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Read data
```{r}
library(data.table)
df <- fread('PS1-4003988.csv')
```
1.a.i
```{r}
#encode gender
df[, gendercode := ifelse(gender == 'female', 1, 0)]
#randomizarion check on gender
gender_check <- lm(gendercode ~ Treatment, data = df)
summary(gender_check)
```
```{r}
standard_error <- function(x) sd(x) / sqrt(length(x))
treatment <- df[Treatment == 1, ]
control <- df[Treatment == 0, ]

#95%CI
lower <- (mean(treatment$gendercode) - mean(control$gendercode)) - 1.96* sqrt((standard_error(treatment$gendercode))^2 + (standard_error(control$gendercode))^2)
upper <- (mean(treatment$gendercode) - mean(control$gendercode)) + 1.96* sqrt((standard_error(treatment$gendercode))^2 + (standard_error(control$gendercode))^2)

print(lower)
print(upper)
```

1.a.ii

The regression summary shows that after we encoded the gender variable, the absolute difference between the treatment and contol group is small. The p-value is large enough (0.484>0.050) to prove that the difference of gender between the treatment and control is not statistically significant and passes the randomization check. 

1.b.i
```{r}
#randomization check on past sales
pastsale_check <- lm(past_sales ~ Treatment, data = df)
summary(pastsale_check)
```
```{r}
#95%CI
lower1 <- (mean(treatment$past_sales) - mean(control$past_sales)) - 1.96* sqrt((standard_error(treatment$past_sales))^2 + (standard_error(control$past_sales))^2)
upper1 <- (mean(treatment$past_sales) - mean(control$past_sales)) + 1.96* sqrt((standard_error(treatment$past_sales))^2 + (standard_error(control$past_sales))^2)

print(lower1)
print(upper1)
```

1.b.ii

The regression summary shows that the absolute difference of past sales between the treatment and contol group is very small. The p-value is large enough (0.762>0.050) to prove that the difference of past sales between the treatment and control is not statistically significant and passes the randomization check. 

2.
```{r}
x <- treatment$sales
xs <- standard_error(x)
x1 <- control$sales
x1s <- standard_error(x1)

#average Intention-to-Treat estimate: 95% CI
lower_itt <- (mean(treatment$sales) - mean(control$sales)) - 1.96* sqrt(xs^2 + x1s^2)
upper_itt <- (mean(treatment$sales) + mean(control$sales)) + 1.96* sqrt(xs^2 + x1s^2)
print(lower_itt)
print(upper_itt)
```
Since the 95% confidence interval does not include 0, meaning that the experiment effect is significantly different from 0 at the 0.05 level. The intent-to-treat estimate is between 0.037 and 2.946. 

```{r}
temp <- lm(sales ~ Treatment, data=df)
summary(temp)
```

3.a
```{r}
treatment_ep <- treatment[saw_ads == 1,]
control_ep <- control[saw_ads == 1,]

#95%CI
lower_ep <- (mean(treatment_ep$gendercode) - mean(control_ep$gendercode)) - 1.96* sqrt((standard_error(treatment_ep$gendercode))^2 + (standard_error(control_ep$gendercode))^2)
upper_ep <- (mean(treatment_ep$gendercode) - mean(control_ep$gendercode)) + 1.96* sqrt((standard_error(treatment_ep$gendercode))^2 + (standard_error(control_ep$gendercode))^2)

print(lower_ep)
print(upper_ep)
```

3.b
```{r}
#95%CI
lower_ep1 <- (mean(treatment_ep$past_sales) - mean(control_ep$past_sales)) - 1.96* sqrt((standard_error(treatment_ep$past_sales))^2 + (standard_error(control_ep$past_sales))^2)
upper_ep1 <- (mean(treatment_ep$past_sales) - mean(control_ep$past_sales)) + 1.96* sqrt((standard_error(treatment_ep$past_sales))^2 + (standard_error(control_ep$past_sales))^2)

print(lower_ep1)
print(upper_ep1)
```

4.
```{r}
#average TOT estimate: 95%CI
lower_tot <- (mean(treatment_ep$sales) - mean(control_ep$sales)) - 1.96* sqrt((standard_error(treatment_ep$sales))^2 + (standard_error(control_ep$sales))^2)

upper_tot <- (mean(treatment_ep$sales) + mean(control_ep$sales)) + 1.96*
sqrt((standard_error(treatment_ep$sales))^2 + (standard_error(control_ep$sales))^2)

print(lower_tot)
print(upper_tot)
```
less noisy, ITT estimate is noisier than TOT estimate. With valid control ads, we get the more precise estimate (TOT)

5.a
```{r}
#ITT
itt_lower <- lower_itt*control[,.N]

itt_upper <- upper_itt*control[,.N]
```

6.
```{r}
treatment_n <- treatment[saw_ads == 0,]

lower_ob <- (mean(treatment_ep$sales) - mean(treatment_n$sales)) - 1.96* sqrt((standard_error(treatment_ep$sales))^2 + (standard_error(treatment_n$sales))^2)

upper_ob <- (mean(treatment_ep$sales) + mean(treatment_n$sales)) + 1.96*
sqrt((standard_error(treatment_ep$sales))^2 + (standard_error(treatment_n$sales))^2)

print(lower_ob)
print(upper_ob)
```
The people who saw the ads and those who didn't see the ads could be quite different from each other. Since the 95% confidence interval contains 0, it means that the ad effect is not statistically different. 

7.
```{r}
ep <- df[saw_ads == 1,]
f <- ep[gendercode == 1,]
m <- ep[gendercode == 0,]
```


```{r}
library(fixest)
n <- feols(sales ~ Treatment, data=f, se='white')
b <- feols(sales ~ Treatment, data=m, se='white')
total <- feols(sales ~ Treatment*gendercode, data=ep, se='white')
etable(n,b,total)
```



































